\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,fullpage}
\newcommand{\Chi}{\mathbf{1}}
\begin{document}

\section*{Lemma (Beurling--Selberg insertion, circle model)}
Let $\beta>0$ and $\Delta\ge1$, $N=\lfloor\Delta\rfloor$. Let $S^\pm$ be the Selberg trigonometric polynomials with
Fourier support $\{|n|\le N\}$ such that on one period $T=\mathbb{R}/\mathbb{Z}$ we have
\[
  S^-(x) \le \Chi_{[-\beta,\beta]}(x) \le S^+(x)\qquad(\forall x\in T),
\]
and $L^1$ errors $E_\pm \approx 1/(N+1)$ (exact in the unforced Selberg pair). In our numerical construction we enforce
pointwise majorant/minorant on a dense grid using Fejér-bumps (still band-limited), which preserves the support
$\{|n|\le N\}$ and induces $E_\pm^{\text{grid}}\ge 1/(N+1)$.

\medskip
\noindent\textbf{Insertion in the explicit formula (schematic).}
Let $x>0$ and set $y=\frac{\log n - \log x}{2\pi}$ (periodized model).
Then
\[
  \sum_{n\ge1} \Lambda(n)\, \Chi_{[-\beta,\beta]}(y)
  \ \le\ \sum_{n\ge1} \Lambda(n)\, S^+(y)
  \ =\ \sum_{|k|\le N} \widehat{S^+}(k) \sum_{n\ge1} \Lambda(n)\, e^{2\pi i k y}
\]
and analogously for the lower bound with $S^-$. The inner Dirichlet sums are handled via the explicit formula
for $\zeta'/\zeta$, yielding (after routine rearrangements) a decomposition:
\[
  (\text{primes})\ =\ (\text{main})\ +\ (\text{zeros})\ +\ (\text{Gamma})\ +\ (\text{trunc. tail}),
\]
where the ``zeros'' piece is uniformly bounded because $S^\pm$ are band-limited and we control tails by the Part~A constants.

\medskip
\noindent\textbf{Parameters used in this package.}
From the JSON produced in the pipeline:
\begin{itemize}
  \item Selberg (circle): $\beta = \verb|0.08|$, $\Delta=\verb|1100|$, $N=\verb|1100|$,
        with $E_\pm^{\text{theory}} = 1/(N+1)$ and grid values
        $E_+^{\text{grid}}=\verb|0.373939583789|$, $E_-^{\text{grid}}=\verb|0.374358168577|$,
        and certified gaps $\min(S^+-\Chi)=\verb|0.000975595058112|$, $\min(\Chi-S^-)=\verb|0.0016918587843|$.
  \item Part A: $C_{\text{bajo}}=\verb|53.3163320695|$, $(B,\beta_{\rm VK},x_1)=(\verb|150|,\verb|0.00371327349654|,\verb|9E+24|)$,
        piecewise bound for $|\psi(x)-x|$ on $x\ge2$ as in the statement.
  \item (Optional) Under RH: $C_{\rm RH,tot}=\verb|1.92336079464|$ so that
        $|\psi(x)-x|\le C_{\rm RH,tot}\sqrt{x}\log^2 x$ for all $x\ge2$.
\end{itemize}

\medskip
\noindent\textbf{Remark.} The circle model is a numerically robust proxy. For the real-line Paley--Wiener pair
we use the same Fejér-windowing idea with the triangular cutoff; the enforcement step carries over verbatim, preserving
band-limit and giving $L^1$ within a small factor of $1/\Delta$.

\end{document}

